\documentclass[a4paper,10pt,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{green}
\usepackage{hyperref}
\hypersetup{backref,colorlinks=false}
\firstname{Lauren}
\familyname{Thomas}
\address{Rodetorenkaai 1B}{Ghent, 9000}
\email{Contact@ljaytee.me}
\mobile{+32 456 24 43 17}
\begin{document}
\maketitle

\section{Education}
\cventry{2017 - 2022}{The Open University, Milton Keynes, UK}{}{}{}{
BSc (Hons) Natural Sciences (Astronomy and Planetary Sciences)
\begin{description}
Including specific study of Mathematical Methods, Astrophysics, General Relativity, Modern Observational Cosmology, Scientific communication and practical research experience with data analysis using python. 
\end{description}   }

\vspace{2mm}

\cventry{2014 - 2016}{North Hykeham Joint Sixth Form}{}{}{}{
\begin{description}
\item [Advanced Level] Physics, Chemistry, Mathematics 
\item [Advanced Subsidiary Level] Further Mathematics, Russian Language and Culture 
\end{description} }

\vspace{2mm}

\cventry{2009--2014}{Sir Robert Pattinson Academy, North Hykeham, UK}{}{}{}{
  General Certificate of Secondary Education - Unweighted GPA: 3.77}

\section{Languages}
\cvlanguage{English}{Fluent}{Native}
\cvlanguage{Russian}{B2/C1}{Advanced Subsidiary Level}
\cvlanguage{French}{B1/B2}{Self Taught}
\cvlanguage{Dutch}{A2/B1}{Self Taught}

\section{Industry Knowledge}

\cvlistitem{Data Analysis \& Visualisation}
\cvlistitem{Scientific Research \& Report Writing}
\cvlistitem{Social media management \& Community Outreach}

\section{Computer \& Programming knowledge}
\cvlistitem{Python 3 - \textit{Data Analysis using scientific python using Jupyter and PyCharm}}
\cvlistitem{Java - \textit{Self taught}}
\cvlistitem{C - \textit{Self taught}}
\cvlistitem{HTML, CSS, SQL \& Javascript}
\cvlistitem{Linux - \textit{Personal usage}}
\cvlistitem{Windows 95 - 11, Microsoft Office 365, Active Directory, Powershell}
\cvlistitem{G-Suite - \textit{Usage \& administration}}

\newpage 

\section{Employment Experience}

\cventry{November 2020 - May 2022}{Warehouse Operative}{Katoen Natie - Synergie}{Oostakker, Belgium}{\textit{Student Job}}{
As a Warehouse Operative, I played a vital role in the administration side of warehouse operations. My responsibilities included compiling, labelling, and invoicing orders. During this time, I had the opportunity to work across multiple sites, serving esteemed clients such as Volvo, Nespresso, Nilfisk, BRP, and Delhaize.}

\vspace{2mm}

\cventry{September 2021 - October 2021}{Project management}{Green Urban Projects}{Ghent, Belgium}{\textit{Student Job - Internship}}{During my internship at Green Urban Projects, I had the opportunity to work directly with the CEO on a business restructuring initiative. This project focused on optimizing operations within their real estate management and property development ventures in Belgium.}

\vspace{2mm}

\cventry{June 2021 - September 2021}{Front of House}{Patrick Foley's}{Ghent, Belgium}{\textit{Student Job}}{As a member of the front of house team at Patrick Foley's, I played a key role in ensuring excellent customer experiences. My responsibilities included opening and closing the restaurant, serving customers as a waitress and bartender, handling cash transactions, and training new staff members.}


\vspace{2mm}

\cventry{September 2020 - June 2021}{Front of House Coordinator}{HornOKPlease - Blerco BVBA}{Ghent, Belgium}{\textit{
Student Job}}{
As the Front of House Coordinator at HornOKPlease, I held the key responsibilities of opening and closing the restaurant and ensuring smooth operations. I successfully coordinated the Front of House team, including conducting interviews and providing training to new hires. Additionally, I took charge of inventory management, stocktaking, auditing, and ordering. \\ One of my crucial roles was to ensure compliance with EU health and safety regulations, as well as EU hygiene and food safety legislation. By diligently adhering to these standards, I contributed to maintaining a safe and hygienic environment for both staff and customers.}

\vspace{2mm}  

\cventry{February 2020 - July 2020}{Assistant General Manager}{Le Bab restaurant group}{Covent Garden - London, UK}{}{
Initially hired as a shift manager with the opportunity for promotion, I quickly progressed to the role of Assistant General Manager. As part of my responsibilities, I efficiently managed opening and closing operations, ensuring the smooth functioning of the establishment. \\ Unfortunately, due to the challenging circumstances brought about by the COVID-19 pandemic, I was placed on the UK government's COVID furlough scheme. Regrettably, the company made the decision to close one of their locations, resulting in my redundancy in July 2020.}
  
\vspace{2mm}

\cventry{August 2019 - February 2020}{Head Waitress}{Gordon Ramsay Restaurants}{Chelsea - London, UK}{}{As a Head Waitress at Gordon Ramsay Restaurants, I played a crucial role in supporting and later managing lunch and dinner services across multiple prestigious venues in London, including Michelin-starred restaurants. During this time, I also gained valuable experience as a bartender, which allowed me to develop a strong understanding of cocktail bartending principles and drink development. Additionally, I had the opportunity to attend introductory (in-house) sommelier training. \\ My responsibilities extended beyond service delivery. I was in charge of front-of-house ordering, inventory management, and completion of stocktaking and auditing. As a Head Waitress, I oversaw the on-the-job evaluations for potential new hires, ensuring that the team maintained the highest standards of service excellence.}

\cventry{March 2018 - July 2019}{Junior Sous Chef -  Patisserie}{John Lewis and Partners}{London, UK}{}{At John Lewis and Partners, I began my journey as a Demi Chef de Partie in the patisserie kitchen of an in-store restaurant. Through dedication and skill, I quickly progressed to the role of Chef de Partie. During this time, I gradually took on more responsibility and eventually handled solo openings of the kitchen for a couple of days each week.}

\vspace{2mm}

\cventry{April 2014 - March 2018}{Kitchen Team Leader}{Cathedral Restaurants LTD}{Lincoln, UK}{}{I started my journey with Cathedral Restaurants LTD as the equivalent of a commis waiter and kitchen porter in 2014. Through my dedication and hard work, I was quickly promoted to the roles of staff trainer and kitchen floor manager within a year. \\ In my position as a Kitchen Team Leader, I successfully managed teams of up to 10 staff members during breakfast and weekend lunch services. I took pride in ensuring smooth kitchen operations and maintaining high standards of food preparation and service. As a staff trainer, I played a pivotal role in onboarding and developing new team members, fostering a culture of continuous learning and growth.}


\section{Voluntary Experience}

\cventry{June 2020 - January 2023}{Board member}{\textit{Elected office}}{Hackerspace.gent}{Gent, Belgium}{During my tenure as an elected board member of Hackerspace.gent, a non-profit organization, I held a crucial role in overseeing the financial aspects of the organization. I diligently managed the finances, ensuring transparency and accountability. \\ Additionally, I played an instrumental role in organizing our annual conference, Newline. Through effective coordination and planning, I contributed to the success of this significant event, which brought together enthusiasts and professionals from the tech community.}

\vspace{2mm}

\cventry{September 2017 - June 2018}{Constituency Youth Officer}{\textit{Elected Office}}{Lincoln Constituency Labour Party (UK)}{Lincoln, UK}{During my tenure as a Constituency Youth Officer, I actively managed the social media presence of the local party on platforms such as Facebook and Twitter. By curating engaging content and facilitating online discussions, I successfully promoted the party's initiatives and values to a wider audience. \\ Additionally, I played a key role in organizing fundraising and community outreach events, with a specific focus on engaging the local student population. One of my notable achievements was assisting with the establishment of "Politics and Pint nights," which became a popular platform for fostering political discussions and engaging young voters in the run-up to the 2018 Local elections. \\ In my capacity as a lay delegate to the local council, I contributed to shaping policy decisions at the local party level. By actively participating in discussions and representing the interests of the party's constituents, I played a vital role in ensuring that the party's policies aligned with the needs and aspirations of the local community.}

\vspace{2mm}

\cventry{July 2017 - March 2018}{Ward Membership Officer}{\textit{Elected Office}}{Lincoln Constituency Labour Party (UK)}{Lincoln, UK}{During my tenure as a Ward Membership Officer, I undertook various responsibilities to strengthen and engage the party's membership within the ward. \\ One of my key accomplishments was creating a comprehensive database of ward members to effectively track their membership dues and ensure timely payments. This system allowed for efficient membership management and improved financial accountability. \\ I also played a crucial role in organizing and coordinating campaigning and canvassing efforts within the ward in preparation for the June 2017 general election. By mobilizing volunteers and implementing strategic campaign initiatives, we successfully raised awareness and garnered support for the party's candidates. \\ In addition, I proudly served as a delegate to the general committee, representing the interests and concerns of the ward members. By actively participating in committee discussions and decision-making processes, I effectively advocated for the needs and aspirations of our constituents.}
 
\vspace{2mm}

\cventry{January 2015 - March 2016}{Teaching Assistant}{Sir Robert Pattinson Academy,}{North Hykeham, UK}{}{During my time as a Teaching Assistant at Sir Robert Pattinson Academy, I volunteered on a weekly basis to provide support to two Key Stage 4 classes studying towards their double-award General Certificate of Secondary Education in Science, which encompassed biology, chemistry, and physics. \\ Working closely with the teaching staff, I ensured that experimental work was conducted safely and efficiently. By providing assistance during practical sessions, I played a vital role in maintaining a secure and productive learning environment. \\ In addition, I organized targeted revision sessions for students in both years. These sessions were designed to address specific areas of difficulty and help students prepare effectively for their exams. By tailoring the content to their needs, I aimed to boost their confidence and facilitate their academic progress.}

\end{document}